Behavior Driven Development in Haskell

### 2012-05-29 paper.tex
talk about Hspec.

\begin{quote}
\emph{kazu: if this subsection is long, we can remove the following paragraph.}
\end{quote}

The \texttt{describe} function combines a list of specs into a larger spec.  It
can be used to organize a spec as a tree.
Internally, a \texttt{Writer} is used to build up specs in a monadic way.

A spec can be run with the \texttt{hspec} function.  When a spec is
run, all properties and examples are evaluated, and failing properties
and examples are reported to the developer.

\begin{quote}
    TBD:
\begin{itemize}
    \item Motivate \verb|test-shouldbe|

        BDD frameworks use \emph{should} or \emph{must} instead of
        \emph{assert}.

        Here is an example that uses RSpec.

        \begin{verbatim}
23.should eq(23)
        \end{verbatim}

        RSpec provides a mechanism to expect exceptions.

>>>>

\begin{quote}
\emph{kazu: How implemneted the ``property'' function? Trystan or Simon?}
\end{quote}

The \texttt{describe} function combines a list of specs into a larger spec.
%% It can be used to organize a spec as a tree.
%% Internally, a \texttt{Writer} is used to build up specs in a monadic way.
A spec can be run with the \texttt{hspec} function.  When a spec is
run, all properties and examples are evaluated, and failing properties
and examples are reported to the developer.

One problem of the original Hspec is that it still uses HUnit
assertions (e.g. verb|@?=| in the example above) , which are TDD
terminologies. In BDD, they are replaced with design terminologies,
{\it expectation}.
The following Rspec example shows the ``should'' expectation keyword:

\begin{quote}
\small
\begin{verbatim}
23.should eq(23)
\end{verbatim}
\end{quote}

\begin{quote}
    TBD:
\begin{itemize}
    \item RSpec provides a mechanism to expect exceptions.
